Cache Oblivious B-trees

### 2011-12-08 paper.tex
Adding the figures

\usepackage{paralist}

@@

\maketitle
\begin{abstract}
Fill me in
\end{abstract}

@@

\subsection{Structure}
\label{sec:structure}

\subsection{Layout}
\label{sec:layout}

@@

The shuttle tree is similar in layout and structure as the original CO B-Tree.
It uses a strongly weight-balanced search tree described previously (see
Section~\ref{sec:structure}) that is laid out in a vEB layout into a PMA. A
notable difference is that the CO B-tree splits the tree at height $h/2$ when
creating the vEB layout while the shuttle tree splits at height $F_k$ where
$F_k$ is the $kth$ Fibonacci number that is stickily less than the height of
the tree. Thus if a tree's height happens to be a Fibonacci number, $F_k$,
then the shuttle tree will choose to split the tree at height $F_{k-1}$. The
top and bottom ``halves'' produced by this split are organized just like
before and shown in Figure ???.

The shuttle tree improves the efficiency of insertion by adding buffers to
each node in the tree. In fact, shuttle tree nodes have a linked list of
buffers rather than a single buffer like BRT and each of these buffers is
another shuttle tree. The length of a node's linked list is related to the
node's height in the tree. A node has a buffer for every time it the leaf of a
sub trees that is split when creating the vEB layout. This idea is illustrated
in Figure ???.

>>>>

\usepackage{paralist}
\usepackage{graphicx}

@@

\maketitle
\begin{abstract}

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\end{abstract}

@@

Bender et al. first introduced a cache oblivious B-tree (CO B-tree) in \cite{cob tree}. The
CO B-tree was able to match the optimum search bound of $\Theta(log_B N)$ memory transfers 
without including any memory-specific parameterization describe the speed or sizes
of the machines memory hierarchy.

The CO B-tree is able to achieve this bound by structuring its elements as a strongly weight-balanced
search tree (SWBST). The SWBST is then laid out into a packed memory array (PMA) using a van Emde Boas (vEB) layout.

\subsection{Structure - SWBST}
\label{sec:structure}

\subsection{Layout - PMA}
\label{sec:layout}

\begin{figure}

\begin{center}
	\includegraphics[width=0.8\columnwidth]{figures/veb.png}
\end{center}

\caption{An illustration of the van Emde Boas (vEB) layout}
\label{fig:veb}
\end{figure}

@@

The shuttle tree is similar in layout and structure as the original CO B-Tree.
It uses a strongly weight-balanced search tree described previously (see
Section~\ref{sec:structure}) that is laid out in a vEB layout into a PMA. A
notable difference is that the CO B-tree splits the tree at height $h/2$ when
creating the vEB layout while the shuttle tree splits at height $F_k$ where
$F_k$ is the $kth$ Fibonacci number that is stickily less than the height of
the tree. Thus if a tree's height happens to be a Fibonacci number, $F_k$,
then the shuttle tree will choose to split the tree at height $F_{k-1}$. The
top and bottom ``halves'' produced by this split are organized just like
before and shown in Figure \ref{fig:veb}.

\begin{figure}

\begin{center}
	\includegraphics[width=0.8\columnwidth]{figures/veb.png}
\end{center}

\caption{An illustration of how the shuttle tree determines the size of a node's linked list}
\label{fig:buffers}
\end{figure}

The shuttle tree improves the efficiency of insertion by adding buffers to
each node in the tree. In fact, shuttle tree nodes have a linked list of
buffers rather than a single buffer like BRT and each of these buffers is
another shuttle tree. The length of a node's linked list is related to the
node's height in the tree. A node has a buffer for every time it the leaf of a
sub trees that is split when creating the vEB layout. This idea is illustrated
in Figure \ref{fig:buffers}.
